{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
Small correction

	To exploit the regularity of the curves of the spectra, we introduced different basis functions in Section \ref{bases} and demonstrated the importance of the truncation parameter $K$ for the estimation in Section \ref{Scalar_on_function_regression}. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC's, which is possibly affected by $K$, by ten-fold cross-validation using the prediction mean-squared error. {\color{red} This is incorrect, nearly nobody does this.} While cross-validation is common for selecting $K$, the number of FPC's is in practice chosen by using the lowest number of FPC's that explain a specified amount of variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}). This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.\\

>>>>

	To exploit the regularity of the curves of the spectra, we introduced different basis functions in Section \ref{bases} and demonstrated the importance of the truncation parameter $K$ for the estimation in Section \ref{Scalar_on_function_regression}. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC's, which is possibly affected by $K$, by ten-fold cross-validation using the prediction mean-squared error. {\color{red} This is incorrect, nearly nobody does this.} While cross-validation is common for selecting $K$, the number of FPC's is in practice chosen by using the lowest number of FPC's that explain a specified amount of variability (cf. \cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (cf. \cite{Jolliffe_1982}). This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.\\
